### 2017-02-01 local-capability-machine.tex
Changed pub future world to be able to go from revoked to temp region
proof of standard region essential lemmas

The two \emph{private future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v,s',\phi_\pub',\phi',H') \futurestr (v',s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}
The two \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v,s',\phi_\pub',\phi',H') \futurewk (v',s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

@@

\subsubsection{Standard regions}
\begin{lemma}
  \label{lem:cap-in-vr-revoketemp-global}
  If
  \begin{itemize}
  \item $\perm \neq \noperm$
  \item $\npair{\stdcap} \in \stdvr(\revokeTemp{W})$
  \end{itemize}
  then 
  \[
    \gl = \glob
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:cap-in-vr-revoketemp-global}]
  Assume for contradiction $\gl = \local$. Procced by case on $\perm$:
  \begin{enumproof}
    \item $\perm = \noperm$\\
      By assumption $\perm \neq \noperm$.
    \item $\perm \in \{ \readonly, \readwrite, \exec, \rwx, \rwl, \rwlx \}$ \\
      Here 
      \[
        \npair{(\start,\addrend)} \in \readCond{}(local)(\revokeTemp{W})
      \]
      must hold, but there are no $\temp$ regions and 
      \[
        r \in \localityReg(\local,\revokeTemp)
      \]
      must be the region name of a $\temp$ region, so no such $r$ exists. (contradiction)
    \item $\perm = \entry$ \\
      % TODO!!! I am not sure it is possible to show for this case.
    \end{enumproof}
\end{proof}

\begin{lemma}
  If
  \[
    \npair{w} \in \stdvr(\revokeTemp{W})
  \]
  then
  \[
    \npair{w} \in \stdvr(W)
  \]
\end{lemma}

\begin{lemma}
  \label{lem:nwl-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \addr, \addrend \in \Addrs \ldotp  \\
    & \quad \iota^\nwl_{\start,\addrend} \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:nwl-subset-pwl}]

\begin{lemma}
  \label{lem:nwlp-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \addr, \addrend \in \Addrs \ldotp  \\
    & \quad \iota^{\nwl,p}_{\start,\addrend}  \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:nwlp-subset-pwl}]

\begin{lemma}
  \label{lem:stau-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \addr, \addrend \in \Addrs \ldotp \forall v \in \{\perma, \temp\} \ldotp \\
    & \quad \dom(\ms) = [\star,\addrend] \Rightarrow \\
    & \qquad \iota^{\sta,u}_{\start,\addrend}(v,\ms) \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stau-subset-pwl}]

@@

\subsubsection{Future worlds}
\begin{lemma}
  For all $W$, $W'$, and $W''$
  \begin{itemize}
  \item $W' \futurewk W \Rightarrow W' \futurestr W$
  \item $\wrev{W} \futurestr W$
  \end{itemize}
  Combined with transitivity of $\futurestr$, the above gives us:
  \begin{itemize}
  \item $W'' \futurestr W' \land W' \futurewk W \Rightarrow W'' \futurestr W$
  \item $W'' \futurewk W' \land W' \futurestr W \Rightarrow W'' \futurestr W$
  \end{itemize}
\end{lemma}

>>>>

The two \emph{private future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurestr (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}
The two \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurewk (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ (\temp,s,\phi_\pub,\phi,H) \in \Regions }
  { (\temp,s,\phi_\pub,\phi,H) \futurewk \revoked }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

@@

\subsubsection{Standard regions}
\begin{lemma}
  \label{lem:revoketemp-readcond}
  If
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(\revokeTemp{W})
  \]
  then
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:revoketemp-readcond}]
  \[
    \npair{(\start,\addrend)} \in \readCond{}(\gl)(\revokeTemp{W})
  \]
  Gives $r \in \localityReg(\gl,\revokeTemp{W})$ such that
  \[
    \forall [\start',\addrend'] \subseteq [\start,\addrend] \ldotp \revokeTemp{W}(r) \nsubsim[n-1] \iota^\pwl_{[\start',\addrend']}
  \]
  Notice $\revokeTemp{W}(r)$ is a $\perma$ region, so $\revokeTemp{W}(r) = W(r)$. Using $r$ as witness, the result is immidiate.
\end{proof}

\begin{lemma}
  \label{lem:revoketemp-writecond}
  If
  \[
    \npair{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(\revokeTemp{W})
  \]
  then
  \[
    \npair{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:revoketemp-writecond}]
  \[
    \npair{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(\revokeTemp{W})
  \]
  Gives $r \in \localityReg(\gl,\revokeTemp{W})$ such that
  \[
    \forall [\start',\addrend'] \subseteq [\start,\addrend] \ldotp \revokeTemp{W}(r) \nsupsim[n-1] \iota_{[\start',\addrend']}
  \]
  Notice $\revokeTemp{W}(r)$ is a $\perma$ region, so $\revokeTemp{W}(r) = W(r)$. Using $r$ as witness, the result is immidiate.
\end{proof}

\begin{lemma}
  \label{lem:revoketemp-execcond}
  If
  \begin{itemize}
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\gl)(\revokeTemp{W})$
  \end{itemize}
  then
  \[
    \npair{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:revoketemp-execcond}]
  Use Lemma~\ref{lem:rt-w-pub-future-w}.
\end{proof}

\begin{lemma}
  \label{lem:revoketemp-entercond}
  If
  \begin{itemize}
  \item $\npair{(\addr,\start,\addrend)} \in \execCond{}(\gl)(\revokeTemp{W})$
  \end{itemize}
  then
  \[
    \npair{(\addr,\start,\addrend)} \in \execCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:revoketemp-entercond}]
    Use Lemma~\ref{lem:rt-w-pub-future-w}.
\end{proof}

\begin{lemma}
  \label{lem:revoketemp-vr-implies-vr}
  If
  \[
    \npair{w} \in \stdvr(\revokeTemp{W})
  \]
  then
  \[
    \npair{w} \in \stdvr(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:revoketemp-vr-implies-vr}]
  Follows from Lemma~\ref{lem:revoketemp-readcond}, Lemma~\ref{lem:revoketemp-writecond}, Lemma~\ref{lem:revoketemp-execcond}, and Lemma~\ref{lem:revoketemp-entercond}.
\end{proof}

\begin{lemma}
  \label{lem:hwnl-nsubset-hpwl}
  \[
    H^\nwl_{\start,\addrend} \; s\; \hat{W} \nsubseteq H^\pwl_{\start,\addrend} \; s\; \hat{W}
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:hwnl-nsubset-hpwl}]
  Let
  \[
    \npair{\ms} \in H^\nwl_{\start,\addrend} \; s\; \hat{W}
  \]
  and show
  \[
    \npair{\ms} \in H^\pwl_{\start,\addrend} \; s\; \hat{W}
  \]
  From the assumption, we get $\dom(\ms) = [\start,\addrend]$. We further need to show
  \[
    \forall \addr \in \dom(\ms) \ldotp \npair[n-1]{\ms(\addr)} \in \stdvr(\xi(\hat{W}))
  \]
  Given $\addr$, we know from the assumption that
  \[
    \npair[n-1]{\ms(\addr)} \in \stdvr(\revokeTemp{\xi(\hat{W})})
  \]
  Now the desired reulst follows from Lemma~\ref{lem:revoketemp-vr-implies-vr}.
\end{proof}

\begin{lemma}
  \label{lem:nwl-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \start, \addrend \in \Addrs \ldotp  \\
    & \quad \iota^\nwl_{\start,\addrend} \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:nwl-subset-pwl}]
  Let $n$, $\start$, $\addrend$ be given and show
  \[
    \iota^\nwl_{\start,\addrend} \nsubsim \iota^\pwl_{\start,\addrend}
  \]
  They agree on the state and transition systems, so given $\hat{W}$ it suffices to show
  \[
    H^\nwl_{\start,\addrend} \; 1\; \hat{W} \nsubseteq H^\pwl_{\start,\addrend} \; 1\; \hat{W}  
  \]
  which is true by Lemma~\ref{lem:hwnl-nsubset-hpwl}.
\end{proof}

\begin{lemma}
  \label{lem:nwlp-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \start, \addrend \in \Addrs \ldotp  \\
    & \quad \iota^{\nwl,p}_{\start,\addrend}  \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:nwlp-subset-pwl}]
  Follows from Lemma~\ref{lem:hwnl-nsubset-hpwl}.
\end{proof}

\begin{lemma}
  \label{lem:stau-subset-pwl}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \start, \addrend \in \Addrs \ldotp \forall v \in \{\perma, \temp\} \ldotp \\
    & \quad \dom(\ms) = [\start,\addrend] \Rightarrow \\
    & \qquad \iota^{\sta,u}_{\start,\addrend}(v,\ms) \nsubsim \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stau-subset-pwl}]
  Essentially the same as the proof of Lemma~\ref{lem:nwl-subset-pwl} and Lemma~\ref{lem:hwnl-nsubset-hpwl}.
\end{proof}

@@

\subsubsection{Future worlds}
\begin{lemma}[World public future world of revoked world]
  \label{lem:rt-w-pub-future-w}
  \[
    \forall W \ldotp \revokeTemp{W} \futurewk W
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:rt-w-pub-future-w}]
  For all $r$ where $W(r) = (\temp,s,\phi_\pub,\phi,H)$, we have $\revokeTemp{W} = \revoked$. By the public future region relation we have
  \[
    W(r) = (\temp,s,\phi_\pub,\phi,H) \futurewk \revokeTemp{W}(r) = \revoked
  \]
  all other regions remain unchanged, so this follows by reflexivity of the public future region relation.
\end{proof}

\begin{lemma}
  For all $W$, $W'$, and $W''$
  \begin{itemize}
  \item $W' \futurewk W \Rightarrow W' \futurestr W$
  \item $\wrev{W} \futurestr W$
  \end{itemize}
  Combined with transitivity of $\futurestr$, the above gives us:
  \begin{itemize}
  \item $W'' \futurestr W' \land W' \futurewk W \Rightarrow W'' \futurestr W$
  \item $W'' \futurewk W' \land W' \futurestr W \Rightarrow W'' \futurestr W$
  \end{itemize}
\end{lemma}
